Informative Oceanographic Sampling using Excursion Probabilities for Multivariate Random Fields

### 2019-09-14 main_new.tex
updates

We calculate EPs and the Bernoulli variance for a few bivariate Gaussian distributions to illustrate concepts. 
Fig. \ref{illus_bivarDens}
shows contour plots of three different densities with increasing correlation $\gamma$ between temperature and salinity. 
\begin{figure}[h!] \centering
  \includegraphics[width=0.99\textwidth]{Figures/illus_bivar.eps}
  \caption{Density contour plots having different correlations between
    temperature and salinity. The densities have unit variance and the thresholds are identical to the mean values $5^o C$ and $30 mg/l$.}\label{illus_bivarDens} 
\end{figure}
Here, the thresholds are set equal to the mean, $\mu_a=t_a=5^o C$ and salinity $\mu_b=t_b=30$ mg/l. The displayed densities have unit standard deviations for both temperature and salinity, but we also study the effect of doubling the standard deviations.

@@

\begin{table}[!h] \centering \caption{EP and Bernoulli variance for different correlations and variances (top rows), and expected Bernoulli variances for both data 
    and only for temperature (bottom rows).}
  \begin{tabular}{c|ccc|ccc}
 &\multicolumn{3}{c}{$\sigma_b=\sigma_a=1$} & \multicolumn{3}{c}{$\sigma_b=\sigma_a=2$} \\
\hline
Correlation $\gamma$ & 0.2 & 0.6 & 0.8 & 0.2 & 0.6 & 0.8 \\
\hline
$p$ & 0.28 & 0.35 & 0.40 & 0.28 & 0.35 & 0.40 \\ 
$p(1-p)$ & 0.20 & 0.23 & 0.24 & 0.20 & 0.23 & 0.24 \\ 
$E_{(y_a,y_b)}(p (1-p))$ & 0.092 & 0.089 & 0.085 & 0.052 & 0.051 & 0.049 \\ 
$E_{y_a}(p (1-p))$ & 0.151 & 0.138 & 0.123 & 0.137 & 0.114 & 0.093 \\ 
\hline
\end{tabular}
\label{tab:sim_rhoab}
\end{table}

>>>>

We calculate EPs and the Bernoulli variance for a few bivariate
Gaussian distributions to illustrate the concepts articulated above.
Fig. \ref{illus_bivarDens} shows contour plots of three different
densities with increasing correlation $\gamma$ between temperature and
salinity.
\begin{figure}[h!] \centering
  \includegraphics[width=0.99\textwidth]{Figures/illus_bivar.eps}
  \caption{Density contour plots having different correlations between
    temperature and salinity. The densities have unit variance and the
    thresholds are identical to the mean values $5^o C$ and
    $30 mg/l$. x-axis is temperature and y-axis is salinity.}
\label{illus_bivarDens}
\end{figure}
Here, the thresholds are set equal to the mean, $\mu_a=t_a=5^o C$ and
salinity $\mu_b=t_b=30$ mg/l. The displayed densities have unit
standard deviations for both temperature and salinity, but we also
study the effect of doubling the standard deviations.

@@

\begin{table}[!h] \centering \caption{EP and Bernoulli variance for
    different correlations and variances (top rows), and expected
    Bernoulli variances for both data \kc{Do you mean an update of the
      data?} and only for temperature (bottom
    rows).}
  \begin{tabular}{c|ccc|ccc}
 &\multicolumn{3}{c}{$\sigma_b=\sigma_a=1$} & \multicolumn{3}{c}{$\sigma_b=\sigma_a=2$} \\
\hline
Correlation $\gamma$ & 0.2 & 0.6 & 0.8 & 0.2 & 0.6 & 0.8 \\
\hline
$p$ & 0.28 & 0.35 & 0.40 & 0.28 & 0.35 & 0.40 \\ 
$p(1-p)$ & 0.20 & 0.23 & 0.24 & 0.20 & 0.23 & 0.24 \\ 
$E_{(y_a,y_b)}(p (1-p))$ & 0.092 & 0.089 & 0.085 & 0.052 & 0.051 & 0.049 \\ 
$E_{y_a}(p (1-p))$ & 0.151 & 0.138 & 0.123 & 0.137 & 0.114 & 0.093 \\ 
\hline
\end{tabular}
\label{tab:sim_rhoab}
\end{table}
